Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
emmeans

# Create clean results table using the pooled contrasts
subgroup_effects <- data.frame(
  DR_Severity = pooled_lapse_effects$dr_severity,
  Treatment = pooled_lapse_effects$any_treatment,
  Log_Odds = round(pooled_lapse_effects$estimate, 4),
  SE = round(pooled_lapse_effects$SE, 4),
  CI_Lower = round(pooled_lapse_effects$CI_Lower, 4),
  CI_Upper = round(pooled_lapse_effects$CI_Upper, 4),
  OR = round(exp(pooled_lapse_effects$estimate), 4),
  P_Value = format.pval(pooled_lapse_effects$p.value, digits = 4, eps = 0.0001)
)

>>>>

# Create clean results table using lapse_effects which has all the calculated columns
subgroup_effects <- data.frame(
  DR_Severity = lapse_effects$dr_severity,
  Treatment = lapse_effects$any_treatment,
  Log_Odds = round(lapse_effects$estimate, 4),
  SE = round(lapse_effects$SE, 4),
  CI_Lower = round(lapse_effects$CI_Lower, 4),
  CI_Upper = round(lapse_effects$CI_Upper, 4),
  OR = round(exp(lapse_effects$estimate), 4),
  P_Value = format.pval(lapse_effects$p.value, digits = 4, eps = 0.0001)
)
